---
title: "Complementary Analysis 1 from Fernanda Hansen P. de Moraes Thesis - Cortical folding alterations in humans due to aging and diseases"
author: "Fernanda Hansen Pacheco de Moraes"
date: "30-november-2021"
output:
  html_document: 
    df_print: kable
    fig_caption: yes
    fig_width: 8
    number_sections: yes
    theme: paper
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

Description of the procedures and analysis present in Complementary
Analysis 1, **Methodological robustness of image processing**, at the
Doctorate Thesis presented to the Programa de Pós-Graduação em Ciência
Médicas at the Instituto D'Or de Pesquisa e Ensino as a partial
requirement to obtain the Doctorate Degree

Part of the data used here cannot be shared due to restrictions of the
Ethic Comittee. Data can be shared upon reasonable request to the
corresponding author. To fullfil these limitation, we will generate (in
next versions) random data to simulate the results.

Get in touch with us
([fernandahmoraes\@gmail.com](mailto:fernandahmoraes@gmail.com){.email})
in case any help is needed, our aim is to improve the code as needed!

```{r call packages, message=FALSE, warning=FALSE}
library(readr)
library(tidyverse)
library(lubridate)
library(ggpubr)
library(kableExtra)
library(broom)
```

```{r wd}
## set working directory
setwd("~/GitHub/FHPdeMoraes_thesis/Complementaryanalysis1_modelrobustness")
```

```{r functions, message=FALSE, warning=FALSE}
## define functions

# test angular coeficinet versus theoretical value
test_coef <- function(reg, coefnum, val){
  co <- coef(summary(reg))
  tstat <- (co[coefnum,1] - val)/co[coefnum,2]
  2 * pt(abs(tstat), reg$df.residual, lower.tail = FALSE)
}

# wrap text
wrapper <- function(x, ...) paste(strwrap(x, ...), collapse = "\n")
```

# Import and organize files

```{r importfiles, message=FALSE, warning=FALSE}
# import subjs
tabela_sujeitos <- read_csv("tabela_sujeitos.csv",
                            col_types = cols(...1 = col_skip()))

# subjs age interval
tabela_sujeitos$Age_interval <- cut(tabela_sujeitos$Age,
                                       breaks = c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65, 70, 75, 80, 85, 90, 95, 100),
                                       right = FALSE,
                                       include.lowest = TRUE)

tabela_sujeitos$Age_interval10 <- cut(tabela_sujeitos$Age,
                                         breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100),
                                         right = FALSE,
                                         include.lowest = TRUE)

# Select session 1
tabela_sujeitos <- tabela_sujeitos %>%
  filter(Session == "1") %>%
  dplyr::select(-c(Session))

```

```{r importfiles2, message=FALSE, warning=FALSE}
# import results with default config EE = 15mm
data_longcor_ses1 <- read_csv("data_longcor_ses1.txt") 
```

```{r importfiles3, echo=TRUE, message=FALSE, warning=FALSE}
## new surfaces ----
# import results with other config EE = 5; 20; 30; 50; 75 and 100mm
data_longcor_ses1_5 <- read_csv("data_longcor_ses1_5mm.txt")
data_longcor_ses1_20 <- read_csv("data_longcor_ses1_20mm.txt")
data_longcor_ses1_30 <- read_csv("data_longcor_ses1_30mm.txt")
data_longcor_ses1_50 <- read_csv("data_longcor_ses1_50mm.txt")
data_longcor_ses1_75 <- read_csv("data_longcor_ses1_75mm.txt")
data_longcor_ses1_100 <- read_csv("data_longcor_ses1_100mm.txt")

# create variable EE diameter
data_longcor_ses1 <- data_longcor_ses1 %>%
  mutate(EEdiameter = 15)
data_longcor_ses1_5 <- data_longcor_ses1_5 %>%
  mutate(EEdiameter = 5)
data_longcor_ses1_20 <- data_longcor_ses1_20 %>%
  mutate(EEdiameter = 20)
data_longcor_ses1_30 <- data_longcor_ses1_30 %>%
  mutate(EEdiameter = 30)
data_longcor_ses1_50 <- data_longcor_ses1_50 %>%
  mutate(EEdiameter = 50)
data_longcor_ses1_75 <- data_longcor_ses1_75 %>%
  mutate(EEdiameter = 75)
data_longcor_ses1_100 <- data_longcor_ses1_100 %>%
  mutate(EEdiameter = 100)

# combine dataframes, create new variables, delete unwanted variables-c(

data <-
  full_join(data_longcor_ses1, data_longcor_ses1_5) %>% # combine files
  full_join(data_longcor_ses1_20) %>%
  full_join(data_longcor_ses1_30) %>%
  full_join(data_longcor_ses1_50) %>%
  full_join(data_longcor_ses1_75) %>%
  full_join(data_longcor_ses1_100) %>%
  mutate(
    SUBJ = SubjectID,
    hemi = Hemisphere,
    ROI = "hemisphere",
    method = "CorticalFoldingTool",
    Longitudinal_correction = "yes",
    AvgThickness = AvgCortThickness,
    ExposedArea = SmoothPialArea,
    TotalArea = PialArea,
    TotalFullArea = PialFullArea,
    WhiteSurfArea = WhiteArea,
    GMvolume = GreymatterVol
  ) %>% dplyr::select(
    -c(
      SubjectID,
      Hemisphere,
      AvgCortThickness,
      PialArea,
      SmoothPialArea,
      WhiteArea,
      GreymatterVol
    )
  )

```

```{r importfiles4, message=FALSE, warning=FALSE}
## FS Standard ----
data_h <-
  read_csv("data_h.csv", col_types = cols(...1 = col_skip()))

data_h <- data_h %>%
  mutate(
    SUBJ = str_sub(SUBJ_ID, 1, 7),
    Session = str_sub(SUBJ_ID, 21, 21),
    Longitudinal_correction = ifelse(str_sub(SUBJ_ID, 23, 26) == "long", "yes", "no"),
    SUBJ_ID = str_sub(SUBJ_ID, 9, 38),
    method = "FreeSurferStandard",
    EEdiameter = 15
  ) %>%
  filter(ROI == "hemisphere", Session == "1") %>%
  dplyr::select(-c(Session))
```

```{r organizefiles, message=FALSE, warning=FALSE}
# combine files
dados <- full_join(data, data_h) %>%
  mutate(
    # create new variables
    logAvgThickness = log10(AvgThickness),
    logTotalArea = log10(TotalArea),
    logTotalFullArea = log10(TotalFullArea),
    logExposedArea = log10(ExposedArea),
    logConvexHullArea = log10(ConvexHullArea),
    logWhiteSurfArea = log10(WhiteSurfArea),
    logGMvolume = log10(GMvolume),
    logConvexHullArea = log10(ConvexHullArea),
    localGI = TotalArea / ExposedArea,
    k = sqrt(AvgThickness) * TotalArea / (ExposedArea ^ 1.25),
    K = 1 / 4 * log10(AvgThickness ^ 2)  + log10(TotalArea) - 5 / 4 * log10(ExposedArea),
    S = 3 / 2 * log10(TotalArea) + 3 / 4 * log10(ExposedArea) - 9 /  4 * log10(AvgThickness ^
                                                                                 2) ,
    I = log10(TotalArea) + log10(ExposedArea) + log10(AvgThickness ^ 2) ,
  ) %>%
  dplyr::select(
    -c(
      PialFullArea,
      WhiteFullArea,
      SmoothPialFullArea,
      ConvexHullFullArea,
      PialFullVol,
      WhiteFullVol,
      SmoothPialFullVol,
      BrainSegVolNotVent,
      SUBJ_ID
    )
  ) %>%
  unique() # delete duplicates

# rename hemispheres
dados$hemi[dados$hemi == "left"] <- "L"
dados$hemi[dados$hemi == "right"] <- "R"

# combine tables through subject if and selected only Session 1
dados <- inner_join(tabela_sujeitos, dados)

#rename variables
colnames(dados)[which(names(dados) == "Sexo")] <- "Gender"
colnames(dados)[which(names(dados) == "Idade")] <- "Age"
colnames(dados)[which(names(dados) == "Diagnostico")] <-
  "Diagnostic"

dados$Age <- as.numeric(dados$Age)
dados$Diagnostic <- as.factor(dados$Diagnostic)
dados$Gender <- as.factor(dados$Gender)

# rename diagnostics
dados$Diagnostic <- as.character(dados$Diagnostic)

dados$Diagnostic[dados$Diagnostic == "CONTROLE"] <- "CTL"
dados$Diagnostic[dados$Diagnostic == "CCL"] <- "MCI"
dados$Diagnostic[dados$Diagnostic == "ALZ"] <- "AD"
```

```{r datacleanup, echo=FALSE, message=FALSE, warning=FALSE}
dados_raw <- dados

# clear data from unwanted diagnostics, subjs with no acquisition equipment defined, subjs with Avg Thickness 0... and only hemispheres!!
dados_all <- dados %>% filter(
  Diagnostic == "CTL" |
    Diagnostic == "MCI" |
    Diagnostic == "AD",!is.na(logAvgThickness),
  ExposedArea != 0 |
    !is.na(localGI),!is.infinite(logExposedArea),
  ROI == "hemisphere"
) %>%
  droplevels()

# see which subjects were excluded
# dados_excluidos <- anti_join(dados_raw, dados_all)
# dados_excluidos %>% dplyr::select(c(SUBJ, Age, Gender, Diagnostic))

# use the filtered data
dados <- dados_all

dados$Diagnostic <-
  factor(dados$Diagnostic, levels = c("CTL", "MCI", "AD")) # transform into levels of factors
```

```{r datacleaunp2, echo=TRUE, message=FALSE, warning=FALSE}
# remove subjects who are not in all samples

lista_subjs_CFT_yes <-
  as.data.frame(
    filter(
      dados,
      method == "CorticalFoldingTool",
      Longitudinal_correction == "yes"
    )$SUBJ
  ) %>%
  unique()

colnames(lista_subjs_CFT_yes)[1] <- "SUBJ"

lista_subjs_FS_no <-
  as.data.frame(filter(
    dados,
    method == "FreeSurferStandard",
    Longitudinal_correction == "no"
  )$SUBJ) %>%
  unique()

colnames(lista_subjs_FS_no)[1] <- "SUBJ"

lista_subjs_FS_yes <-
  as.data.frame(filter(
    dados,
    method == "FreeSurferStandard",
    Longitudinal_correction == "yes"
  )$SUBJ) %>%
  unique()

colnames(lista_subjs_FS_yes)[1] <- "SUBJ"

listas <- inner_join(lista_subjs_CFT_yes, lista_subjs_FS_no) %>%
  inner_join(lista_subjs_FS_yes)

dados <- inner_join(dados, listas)

# write.csv(dados, "dados_compmethods.csv")
```

# Table 1

Number of subjects and their mean ages by diagnostic. SD for standard
deviation.

```{r}
dados %>%
  group_by(Diagnostic) %>%
  summarise(N = n_distinct(SUBJ),
            Age = paste(signif(mean(Age), 2), "±", signif(sd(Age), 2))) %>%
  kable(digits = 2) %>%
  kable_styling()
```

# Table 2

Table explaining the processes evaluated in this analysis, totaling
eight possibilities.

```{r}
dados %>%
  group_by(method, Longitudinal_correction, EEdiameter) %>%
  summarise(N = n_distinct(SUBJ)) %>%
  kable(digits = 2) %>%
  kable_styling()
```

# Results

## Testing normality

### Avg Thickness

```{r}
dados %>%
  mutate(method_results = method) %>%
  group_by(Diagnostic,
           method_results,
           Longitudinal_correction,
           EEdiameter) %>%
  do(tidy(shapiro.test(.$AvgThickness))) %>%
  ungroup() %>%
  kable(digits = 2) %>%
  kable_styling()
```

### Total Area

```{r}
dados %>%
  mutate(method_results = method) %>%
  group_by(Diagnostic,
           method_results,
           Longitudinal_correction,
           EEdiameter) %>%
  do(tidy(shapiro.test(.$TotalArea))) %>%
  ungroup() %>%
  kable(digits = 2) %>%
  kable_styling()
```

### Exposed Area

```{r}
dados %>%
  mutate(method_results = method) %>%
  group_by(Diagnostic,
           method_results,
           Longitudinal_correction,
           EEdiameter) %>%
  do(tidy(shapiro.test(.$ExposedArea))) %>%
  ungroup() %>%
  kable(digits = 2) %>%
  kable_styling()
```

### localGI

```{r}
dados %>%
  mutate(method_results = method) %>%
  group_by(Diagnostic,
           method_results,
           Longitudinal_correction,
           EEdiameter) %>%
  do(tidy(shapiro.test(.$localGI))) %>%
  ungroup() %>%
  kable(digits = 2) %>%
  kable_styling()
```

### K

```{r}
dados %>%
  mutate(method_results = method) %>%
  group_by(Diagnostic,
           method_results,
           Longitudinal_correction,
           EEdiameter) %>%
  do(tidy(shapiro.test(.$K))) %>%
  ungroup() %>%
  kable(digits = 2) %>%
  kable_styling()
```

### S

```{r}
dados %>%
  mutate(method_results = method) %>%
  group_by(Diagnostic,
           method_results,
           Longitudinal_correction,
           EEdiameter) %>%
  do(tidy(shapiro.test(.$S))) %>%
  ungroup() %>%
  kable(digits = 2) %>%
  kable_styling()
```

### I

```{r}
dados %>%
  mutate(method_results = method) %>%
  group_by(Diagnostic,
           method_results,
           Longitudinal_correction,
           EEdiameter) %>%
  do(tidy(shapiro.test(.$I))) %>%
  ungroup() %>%
  kable(digits = 2) %>%
  kable_styling()

```

## Comparing the usage of longitudinal correction

```{r}
long_comp <-
  filter(dados,
         method == "FreeSurferStandard",
         !is.na(TotalArea),
         !is.infinite(ExposedArea))

LC_status <- c(yes = "With longitudinal correction",
               no = "Without longitudinal correction")
```

### Figure 1. Model application

```{r}
## Thesis Figure 9 

longcor1 <- ggplot(long_comp,
                   aes(
                     ExposedArea,
                     sqrt(AvgThickness) * TotalArea,
                     color = Diagnostic,
                     fill = Diagnostic
                   )) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
  geom_abline(slope = 1.25,
              intercept = coef(lm(
                log10(TotalArea * sqrt(AvgThickness)) ~ log10(ExposedArea),
                data = dados,
                na.action = na.omit
              ))[1],
              color = "black") +
  theme_pubr() +
  facet_grid(Longitudinal_correction ~ . ,
             labeller = labeller(Longitudinal_correction = LC_status)) +
  labs(color = "Diagnostic",
       fill = "Diagnostic") +
  scale_x_log10() +
  scale_y_log10()

# ggsave("longcor1.png", plot = longcor1, dpi=1200, width = 11, height = 11, units = "cm", device = "png")

longcor1 <- annotate_figure(longcor1,
                            bottom = text_grob(
                              wrapper(
                                "Cortical Folding model with and without the use of longitudinal correction.",
                                width = 100
                              ),
                              face = "italic"
                            ))

longcor1

```

### Slope for each diagnostic

⍺ for each diagnostic with and without longitudinal correction. Slope ± Standard Deviation and 95% Confidence Interval.

```{r}
lm_fit_comp_idor <- long_comp %>%
  group_by(Diagnostic, Longitudinal_correction) %>%
  do(fit_comp_idor = tidy(lm(
    log10(TotalArea * sqrt(AvgThickness)) ~ log10(ExposedArea),
    data = .,
    na.action = na.omit
  ), conf.int = TRUE)) %>%
  unnest(cols = c(fit_comp_idor))

filter(lm_fit_comp_idor, term == "log10(ExposedArea)") %>% kable(digits = 2) %>% kable_styling()
```

#### Plot

```{r}
ggplot(
  data = filter(lm_fit_comp_idor, term == "log10(ExposedArea)"),
  aes(x = Diagnostic,
      y = estimate, color = Longitudinal_correction, )
) +
  geom_point() +
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error)) +
  geom_smooth(method = "lm", se = TRUE) +
  geom_hline(yintercept = 1.25, linetype = "dashed") +
  theme_pubr() +
  labs(y = expression(alpha))
```

### Correlation for each variable within methodologies

Correlations for each morphological variable measured by FreeSurfer before and after the longitudinal correction.

```{r}
long_comp_long <- long_comp %>%
  dplyr::select(
    c(
      SUBJ,
      Diagnostic,
      hemi,
      Longitudinal_correction,
      AvgThickness,
      TotalArea,
      ExposedArea,
      localGI,
      K,
      S,
      I
    )
  ) %>%
  pivot_wider(
    names_from = Longitudinal_correction,
    values_from = c(AvgThickness,
                    TotalArea,
                    ExposedArea,
                    localGI,
                    K,
                    S,
                    I)
  )
```

#### Avg Thickness

```{r}
cor.test(long_comp_long$AvgThickness_no, long_comp_long$AvgThickness_yes)
```

#### Total Area

```{r}
cor.test(long_comp_long$TotalArea_no, long_comp_long$TotalArea_yes)
```

#### Exposed Area

```{r}
cor.test(long_comp_long$ExposedArea_no, long_comp_long$ExposedArea_yes)
```

#### localGI

```{r}
cor.test(long_comp_long$localGI_no, long_comp_long$localGI_yes)
```

#### K

```{r}
cor.test(long_comp_long$K_no, long_comp_long$K_yes)
```

#### S

```{r}
cor.test(long_comp_long$S_no, long_comp_long$S_yes)
```

#### I

```{r}
cor.test(long_comp_long$I_no, long_comp_long$I_yes)
```

## FreeSurfer vs CFT

```{r}
method_comp <- filter(dados, Longitudinal_correction == "yes", EEdiameter == "15")
```

### Figure 2. Model application

```{r}
## Thesis Figure 

FS_CFT1 <- ggplot(method_comp,
                  aes(
                    ExposedArea,
                    sqrt(AvgThickness) * TotalArea,
                    color = Diagnostic,
                    fill = Diagnostic
                  )) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
  geom_abline(slope = 1.25,
              intercept = coef(lm(
                log10(TotalArea * sqrt(AvgThickness)) ~ log10(ExposedArea),
                data = dados,
                na.action = na.omit
              ))[1],
              color = "black") +
  theme_pubr() +
  facet_grid(method ~ .) +
  labs(color = "Diagnostic",
       fill = "Diagnostic") +
  scale_x_log10() +
  scale_y_log10()

# ggsave("FS_CFT1.png", plot = FS_CFT1, dpi = 1200, width = 11, height = 11, units = "cm", device = "png")

FS_CFT1 <- annotate_figure(FS_CFT1,
                           bottom = text_grob(
                             wrapper(
                               "Application of the Mota & Houzel gyrification model (Mota; Herculano Houzel, 2015) with the estimated morphological parameters through standard processing (”FreeSurferStandard”) and extraction using the Cortical Folding Analysis Tool (”CorticalFoldingTool”) (Wang; Ludwig; Mota, 2019).",
                               width = 100
                             ),
                             face = "italic"
                           ))

FS_CFT1

```

### Slope for each diagnostic

⍺ for each diagnostic with and without longitudinal correction. Slope ± Standard Deviation and 95% Confidence Interval.

```{r}
lm_fit_comp_idor <- method_comp %>%
  group_by(Diagnostic, method) %>%
  do(fit_comp_idor = tidy(lm(
    log10(TotalArea * sqrt(AvgThickness)) ~ log10(ExposedArea),
    data = .,
    na.action = na.omit
  ), conf.int = TRUE)) %>%
  unnest(cols = c(fit_comp_idor))

filter(lm_fit_comp_idor, term == "log10(ExposedArea)") %>% kable(digits = 2) %>% kable_styling()

```

#### Plot

```{r}
ggplot(
  data = filter(lm_fit_comp_idor, term == "log10(ExposedArea)"),
  aes(x = Diagnostic,
      y = estimate, color = method)
) +
  geom_point() +
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error)) +
  geom_smooth(method = "lm", se = TRUE) +
  geom_hline(yintercept = 1.25, linetype = "dashed") +
  theme_pubr() +
  labs(y = expression(alpha))
```

### Correlation for each variable within methodologies

Correlations of each average morphological measurement by FreeSurfer and Cortical Folding Analysis Tool. All correlations are robust and with a significant p value.

```{r}
method_comp_long <- method_comp %>%
  dplyr::select(
    c(
      SUBJ,
      Diagnostic,
      hemi,
      method,
      AvgThickness,
      TotalArea,
      TotalFullArea,
      ExposedArea,
      localGI,
      K,
      S,
      I
    )
  ) %>%
  pivot_wider(
    names_from = method,
    values_from = c(
      AvgThickness,
      TotalArea,
      TotalFullArea,
      ExposedArea,
      localGI,
      K,
      S,
      I
    )
  )
```

#### Avg Thickness

```{r}
cor.test(method_comp_long$AvgThickness_FreeSurferStandard, method_comp_long$AvgThickness_CorticalFoldingTool)
```

#### Total Area

```{r}
cor.test(method_comp_long$TotalArea_FreeSurferStandard, method_comp_long$TotalArea_CorticalFoldingTool)
```

#### Exposed Area

```{r}
cor.test(method_comp_long$ExposedArea_FreeSurferStandard, method_comp_long$ExposedArea_CorticalFoldingTool)
```

#### localGI

```{r}
cor.test(method_comp_long$localGI_FreeSurferStandard, method_comp_long$localGI_CorticalFoldingTool)
```

#### K

```{r}
cor.test(method_comp_long$K_FreeSurferStandard, method_comp_long$K_CorticalFoldingTool)
```

#### S

```{r}
cor.test(method_comp_long$S_FreeSurferStandard, method_comp_long$S_CorticalFoldingTool)
```

#### I

```{r}
cor.test(method_comp_long$I_FreeSurferStandard, method_comp_long$I_CorticalFoldingTool)
```

### Difference

At the Cortical Folding Tool, the Total Full Area should be the Total
Area from FreeSurfer.

```{r}
ggplot(data = method_comp_long,
       aes(x = TotalFullArea_CorticalFoldingTool, y = TotalArea_FreeSurferStandard)) +
  geom_point(aes(color = Diagnostic)) +
  geom_smooth(method = "lm", color = "gray") +
  stat_cor() +
  theme_pubr()
```

```{r}
ggplot(
  data = method_comp_long,
  aes(x = TotalFullArea_CorticalFoldingTool - TotalArea_FreeSurferStandard, color = Diagnostic)
) +
  geom_density() +
  theme_pubr() +
  labs(color = "Diagnostic")
```

## Smoother surfaces - different EE diameter

```{r}
diameter_comp <-
  filter(dados,
         Longitudinal_correction == "yes",
         method == "CorticalFoldingTool")
```

### Slope for each diagnostic (plot)
```{r}
lm_fit_comp_idor <- diameter_comp %>%
  group_by(Diagnostic, EEdiameter) %>%
  do(fit_comp_idor = tidy(lm(
    log10(TotalArea * sqrt(AvgThickness)) ~ log10(ExposedArea),
    data = .,
    na.action = na.omit
  ),
  conf.int = TRUE)) %>%
  unnest(cols = c(fit_comp_idor))

# lm_fit_comp_idor %>% kable(digits = 2) %>% kable_styling()
```

```{r}
EEdiameter <-
  ggplot(
    data = filter(lm_fit_comp_idor, term == "log10(ExposedArea)"),
    aes(x = EEdiameter,
        y = estimate)
  ) +
  geom_point() +
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error)) +
  geom_smooth(se = TRUE, color = "black") +
  geom_hline(yintercept = 1.25, linetype = "dashed") +
  theme_pubr() +
  labs(y = expression('Slope (' * alpha * ')'), x = "se sphere diameter [mm]") +
  facet_grid(Diagnostic ~ .) +
  scale_x_continuous(breaks = c(5, 15, 20, 30, 50, 75, 100))

EEdiameter <- annotate_figure(EEdiameter,
                              bottom = text_grob(
                                wrapper(
                                  "Variation of the exposed surface area with the increase of the diameter of the structural element. Increasing the diameter of the structural element (se), in theory, would lead to a smaller area of the exposed surface by this being less sensitive to gyri and sulci. In the figure, we notice that the area becomes constant from 30 mm.",
                                  width = 100
                                ),
                                face = "italic"
                              ))

EEdiameter

# ggsave("EEdiameter.png", plot = EEdiameter, dpi=1200, width = 18, height = 11, units = "cm", device = "png")
```

```{r}
EEdiameter2 <- ggplot(data = diameter_comp,
                      aes(x = EEdiameter,
                          y = ExposedArea,
                          group = EEdiameter)) +
  geom_boxplot() +
  theme_pubr() +
  labs(y = "ExposedArea [mm²]", x = "se sphere diameter [mm]") +
  scale_x_continuous(breaks = c(5, 15, 20, 30, 50, 75, 100))

# ggsave("EEdiameter2.png", plot = EEdiameter2, dpi=1200, width = 18, height = 11, units = "cm", device = "png")

EEdiameter2 <- annotate_figure(EEdiameter2,
                               bottom = text_grob(
                                 wrapper(
                                   "Variation of the slope of the line, called α in the girding model with the increase of the diameter of the structural element (se). Increasing the diameter of the structural element would, in theory, lead to greater robustness of the generated exposed surface, which would be less sensitive to sulci and gyri. In the figure, we notice that from 30 mm, the value of α becomes constant. Bars represent standard deviation.",
                                   width = 100
                                 ),
                                 face = "italic"
                               ))

EEdiameter2

```

# EXTRA

It was not incldued in the thesis, but we also testes wheter a convex hull would be better. Here it goes.

### Convex Hull

```{r}
diameter_comp$EEdiameter <- as.factor(diameter_comp$EEdiameter)

CH <-
  diameter_comp %>%
  filter(EEdiameter == 15) %>%
  mutate(
    EEdiameter = as.factor("ConvelHull"),
    ExposedArea = ConvexHullArea,
    logExposedArea = logConvexHullArea,
    K = 1 / 2 * logAvgThickness + logTotalArea - 5 / 4 * logConvexHullArea ,
    I = logTotalArea + logConvexHullArea  + logAvgThickness ^ 2,
    S = 3 / 2 * logTotalArea + 3 / 4 * logConvexHullArea  - 9 / 4 * logAvgThickness ^ 2
  )

diameter_comp <- full_join(diameter_comp, CH)

```

```{r}
lm_fit_comp_idor <- diameter_comp %>%
  group_by(Diagnostic, EEdiameter) %>%
  do(fit_comp_idor = tidy(lm(
    log10(TotalArea * sqrt(AvgThickness)) ~ log10(ExposedArea),
    data = .,
    na.action = na.omit
  ),
  conf.int = TRUE)) %>%
  unnest(cols = c(fit_comp_idor))

#lm_fit_comp_idor %>% kable(digits = 2) %>% kable_styling()

```

```{r}
ggplot(
  data = filter(lm_fit_comp_idor, term == "log10(ExposedArea)"),
  aes(x = EEdiameter,
      y = estimate)
) +
  geom_point() +
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error)) +
  geom_hline(yintercept = 1.25, linetype = "dashed") +
  theme_pubr() +
  labs(y = expression(alpha), x = "se sphere diameter [mm]") + facet_grid(Diagnostic ~ .)
```

```{r}
ggplot(data = diameter_comp,
       aes(x = EEdiameter,
           y = ExposedArea,
           group = EEdiameter)) +
  geom_boxplot() +
  theme_pubr()
```
